Composition-climate paper

### 2016-08-24 Composition_Ecology.Rmd
Pushing latest `docx` build of the paper, with edits through the results.  Commiting Rmd, it's slightly ahead of the `docx`.

In this study, shifts in realized climate niches and the underlying interactions between climate change and land use emerge from three basic processes.  First, climates have changed over the 20th and early 21st centuries, with rising winter minimum temperatures, declining summer maximum temperatures, and increasing precipitation.  Second, tree species distributions have not yet fully adjusted to these climate changes, causing the environmental niches to shift.  Third, anthropogenic land use has selectively occupied some portions of geographic and environmental space, making these regions less available to tree genera.  Because much of the land-use change within the region occurs in the south, where agricultural conversion has largely eliminated open forests [@rhemtulla2009historical], the effects of climate change and land use are compounding.  Northern species show shifts away from drier habitat, while land-use in the northern prairie-forest margin intensifies, shifting species further than expected along the precipitation gradient. For southern tree species, land-use conversion has primarily occurred along the southern margins of the region, parallel to temperature and precipitation gradients.

Some of these apparent shifts in climate niches may be due to differences in sampling design rather than to actual shifts in species distributions.  In particular, the PLS survey design resulted in more survey points across the landscape than in the FIA dataset, but fewer trees surveyed per point.  The FIA is confined to forested and semi-forested areas because surveys are limited to plots with > 10% tree cover [@woudenberg2010forest].  Hence, the FIA dataset may be underrepresenting tree distributions in unforested or semi-forested regions.  Regardless of cause, the differences between the PLS and FIA tree distributions are important for distributional modeling because FIA data provides the most detailed and most widely used source of tree distributional data over the entire contiguous United States [@wang2016landscape;@nieto2015close;@bell2014early].  Hence, any incompleteness in the representation of realized climate niches based on FIA data may result in inaccurate model projections.

>>>>

In this study, shifts in realized climate niches and the underlying interactions between climate change and land use emerge from three basic processes.  First, climates have changed over the 20th and early 21st centuries, with rising winter minimum temperatures, declining summer maximum temperatures, and increasing precipitation.  These climate changes are produced by a combination of natural variability and anthropogenic change; the latter signal is strongest in the second half of the 20^th^ century and early 21^st^ century [@stocker2013ipcc;@swanson2009long;@estrada2013statistically]. Second, tree species distributions have not yet fully adjusted to these climate changes, causing tree distributions to be in partial disequilibrium with climate [@svenning2013disequilibrium;@williamsinpress] and environmental niches to shift.  Third, anthropogenic land use has selectively occupied some portions of geographic and environmental space, making these regions less available to tree species.  Because much of the land-use change within the region occurs in the south, where agricultural conversion has largely eliminated open forests [@rhemtulla2009historical], the effects of climate change and land use are compounding.  Northern species show shifts away from drier and warmer habitat. Intensification of land-use in the northern prairie-forest margin shifts species further than expected along the precipitation gradient, to apparent wetter climates. For southern tree species, land-use conversion has primarily occurred along the southern margins of the region, parallel to and in the same direction as temperature and precipitation gradients.

Some of these apparent shifts in climate niches may be due to differences in sampling design rather than to actual shifts in species distributions.  In particular, the PLS survey design resulted in more survey points across the landscape than in the FIA dataset, but fewer trees surveyed per point.  The FIA is confined to forested and semi-forested areas because surveys are limited to plots with > 10% tree cover [@woudenberg2010forest].  Hence, the FIA dataset may be underrepresenting tree distributions in unforested or semi-forested regions.  If so, estimates of forest loss (Table 1) and niche shifts (Figures 4 & 5) may be overestimated. Regardless of cause, the differences between the PLS and FIA tree distributions are important for distributional modeling because FIA data provides the most detailed and most widely used source of tree distributional data over the entire contiguous United States [@wang2016landscape;@nieto2015close;@bell2014early].  Hence, any incompleteness in the representation of realized climate niches based on FIA data that are affecting this study should also affect model projections based on FIA data.
